Insert the article title here

### 2020-07-23 tex/results.tex
Finish draft on rockstuhl
fix reference name

We performed a grid independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the z-axis.
(similar to quadratic cylinder on Fig 18 of Rockstuhl et.al). 
Due to the nature of the geometry, and its sharp edges it was challenging to see proper convergence. However,
for this type of physics, convergence has been studied in our previous work \cite{ClementiCooperBarba2019}. 
In the Figure \ref{fig:cube535} we show a grid independence study, where we go from a mesh of 15552 
triangles (density = 1.11x10$^-4$ $N/\text{\AA}$) to 19200 (density = 9.05x10$^-5$ $N/\text{\AA}$) 
triangles and the computed results do not change.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{AR_22_vs_norm.pdf} 
    \caption{ Extinction cross section across wave number for SiC pillars of multiple Aspect ratios. 
             (H=950 nm, W=400nm, L=400-2800 (AR=1-7))
            Normalized by maximum extinction cross section as a function of wave number,
            for a pillar orientation such that the electric field is parallel polarized 
            (I HAVE TO EXPLAIN THIS BETTER, IT ALIGNS WITH THE LENGTH OF THE PILLAR). 
            We present the results for normal incidence and 22 degrees incidence, 
            for different aspect ratios (AR)
            }
    \label{fig:AR_22_vs_norm}
 \end{figure}

>>>>

We performed a grid independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the z-axis.
(similar to quadratic cylinder on Fig 18 of Rockstuhl et.al). 
Due to the nature of the geometry, and its sharp edges it was challenging to see proper convergence. However,
for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. 
In the Figure \ref{fig:cube535} we show a grid independence study, where we go from a mesh of 15552 
triangles (density = 1.11x10$^-4$ $N/\text{\AA}$) to 19200 (density = 9.05x10$^-5$ $N/\text{\AA}$) 
triangles and the computed results do not change.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{AR_22_vs_norm.pdf} 
    \caption{ Extinction cross section across wave number for SiC pillars of multiple Aspect ratios. 
             (H=950 nm, W=400nm, L=400-2800 (AR=1-7))
            Normalized by maximum extinction cross section as a function of wave number,
            for a pillar orientation such that the electric field is parallel polarized 
            (I HAVE TO EXPLAIN THIS BETTER, IT ALIGNS WITH THE LENGTH OF THE PILLAR). 
            We present the results for normal incidence and 22 degrees incidence, 
            for different aspect ratios (AR)}
    \label{fig:AR_22_vs_norm}
 \end{figure}
